DDSAnalytics  - Employee Trends

### 2018-04-10 msds6371-group-project-kaggle.Rmd
Add sample image
Add untransformed plaots and statistics

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
![Kaggle House Prices](images/Kaggle.png)
\pagebreak

@@

#### Plots of Untransformed Data
![Image 001 - BrkSide](images/Untransformed-BrkSide.png)
![Image 002 - Edwards](images/Untransformed-Edwards.png)
![Image 003 - NAmes](images/Untransformed-NAmes.png)
![Image 004 - Other Neighborhoods](images/Untransformed-Others.png)
![Image 005 - MLR Parameter Estimates](images/Untransformed-MLR-Estimates.png)
![Image 006 - MLR Residual Plots](images/Untransformed-MLR-Residuals.png)
